### 2017-02-12 manuscript.rmd
figure scaling

	knitr::kable(
		species_table,
		caption = "Number of tips for each species in trees that were used to calculate the independent contrasts."
	)

@@

				nhx %>% 
					ggtree() + 
					geom_tiplab( aes( label=species ), hjust=-0.1 ) + 
					xlim( NA, 1400 ) + 
					geom_tippoint( aes( size=Tau ) ) +
					geom_nodepoint( aes( color=Event ), shape=15, size = 2 ) +
					geom_tippoint( aes( size=Tau ) ) +
					geom_text( aes( label=round( abs( pic ), 3 ) ), vjust=1.5, hjust=1, size=2.5, col="blue" ) + 
					geom_text( aes( label=clade_name ), vjust=-.5, hjust=1, size=2.5, col="black" ) + 
					theme( legend.position="right" )
			}
		)

>>>>

	knitr::kable(
		species_table,
		caption = "Number of tips N for each species in trees that were used to calculate the independent contrasts."
	)

@@

				nhx %>% 
					ggtree() + 
					geom_tiplab( aes( label=species ), hjust=-0.1 ) + 
					xlim( 0, 400 ) + 
					geom_tippoint( aes( size=Tau ) ) +
					geom_nodepoint( aes( color=Event ), shape=15, size = 2 ) +
					geom_tippoint( aes( size=Tau ) ) +
					geom_text( aes( label=round( abs( pic ), 3 ) ), vjust=1.5, hjust=1, size=2.5, col="blue" ) + 
					geom_text( aes( label=clade_name ), vjust=-.5, hjust=1, size=2.5, col="black" ) + 
					theme( legend.position="right" )
			}
		)
